Benchmarking neuromorphic systems with Nengo

### 2015-07-08 paper/paper.tex
Add paragraph on small / short models
In response to Andrew's comment.

The run time results are of the utmost importance
when evaluating backends for different applications,
especially those that require real-time interaction,
such as robotics. In general, all backends
perform adequately for the three smaller models.
The OpenCL backend is significantly slower for small
models, like the product and controlled oscillator models.
SpiNNaker, on the other hand, is slower than other backends
for these models, because its goal
is to run in real-time even if it is possible to run faster.
The most important result is for the largest model,
the basal ganglia sequence.
In this model, the distilled and Brainstorm backends
performed very poorly
(though neither has speed as a primary goal).
The reference backend also did not perform well,
operating at nearly eight times slower than real-time.
The OpenCL backend performed well, operating at around
four times slower than real-time.
The best performance was seen by the SpiNNaker backend,
however, which operated at around 1.5 times real-time
on this moderately-sized model.
Since the SpiNNaker board always runs at real-time,
this means that around one-third of the time taken
for the \texttt{run} call is overhead.

@@

The most important finding from these benchmarks
is that specialized hardware (including GPUs)
can result in significantly faster run times
for certain models,
with little to no cost in accuracy.
The conditions under which the OpenCL backend
performs slower than the reference backend
(e.g., the product and controlled oscillator models)
bear closer inspection to determine the source
of the slowdown.
Similarly, we should investigate
the model instances in which the SpiNNaker backend
differs from other backends
in the product model.

@@

% ??? Make color palette grey-scale friendly

% ??? figure out these colors!

% ??? Add A B C etc labels to figures

>>>>

The run time results are of the utmost importance
when evaluating backends for different applications,
especially those that require real-time interaction,
such as robotics. In general, all backends
perform adequately for the three smaller models.
The OpenCL backend is significantly slower for small
models, like the product and controlled oscillator models.
SpiNNaker, on the other hand, is slower than other backends
for these models, because its goal
is to run in real-time even if it is possible to run faster.
The most important result is for the largest model,
the basal ganglia sequence.
In this model, the distilled and Brainstorm backends
performed very poorly
(though neither has speed as a primary goal).
The reference backend also did not perform well,
operating at nearly eight times slower than real-time.
The OpenCL backend performed well, operating at around
four times slower than real-time.
The best performance was seen by the SpiNNaker backend,
however, which operated at around 1.5 times real-time
on this moderately-sized model. (??? revisit with new results)
Since the SpiNNaker board always runs at real-time,
this means that around one-third of the time taken
for the \texttt{run} call is overhead.

@@

The most important finding from these benchmarks
is that significant speedups can be gained by
running models on specialized hardware and GPUs,
with little to no cost in accuracy.
The conditions under which the OpenCL backend
performs slower than the reference backend
(e.g., the product and controlled oscillator models)
bear closer inspection to determine the source
of the slowdown.
Similarly, we should investigate
the product model instances
in which the SpiNNaker backend
differs from other backends.

It should be noted that although there are clear
relative speed differences between backends,
these models are very small---each would only
be a small component of a larger model.
Spaun, for example, includes multiple copies
or larger versions of all four of the models
benchmarked here.
Additionally, we run them
for very small amounts of time---the longest
simulation runs for 10 simulated seconds.
Real models run for longer amounts of time
to gather data comparable to those gathered
in neuroscientific experiments.
However, we expect that the results
would be similar, though exaggerated,
in larger models run for longer amount of time.
The distilled and brainstorms backends would
perform slowly, the OpenCL backend should
run faster than the reference backend,
and SpiNNaker will continue to run at real-time.

@@
